Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-22 Ch1_movement_rates/Ch1_Figures.Rmd
Working on Figures 4 and 5 from results

  seed.data %>% 
    drop_na(s.id) %>% 
    mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>% 
    #slice_head(., n = s.size) %>% 
    sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, y = yloc, color = dispcat)) +
      geom_point(alpha = lalpha) +
      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
      geom_text(label = scenario, x = -1000, y = -1000, color = "black") +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw() +
      theme(legend.position = "none",
            axis.title = element_blank()) +
       NULL -> seedlocplot

@@

disp_df %>%
  group_by(., model) %>%
  sample_n(., 10000) %>%
  #mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = av.disp, x = model
                #, color = dispcat
                )) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Average dispersal in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) -> p_dispersal

@@

# ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")

@@

# Figure 5 - seed dispersal kernel parameters
Here we are using the distance of each seed

@@

@@

plot_grid(weib_shape, weib_scale)

@@

>>>>

  seed.data %>% 
    drop_na(s.id) %>% 
    mutate(dispcat = ifelse(disp <150, "non", 
                            ifelse(disp <500, "med", "ldd"))) %>% 
    #slice_head(., n = s.size) %>% 
    sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, y = yloc, color = dispcat)) +
      geom_point(alpha = lalpha) +
      scale_color_manual(values = c(my.cols1[6], my.cols1[7], "black")) +
      geom_text(label = scenario, x = -1100, y = -1100, color = "black") +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw() +
      theme(legend.position = "none",
            axis.title = element_blank()) +
       NULL -> seedlocplot

@@

disp_df %>%
  group_by(., model) %>%
  sample_n(., 10000) %>%
  #mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = av.disp, x = model
                #, color = dispcat
                )) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Average dispersal per run in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) -> p_dispersal

@@

ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")

@@

# Figure 5 - All about the seed dispersal Kernels - Weibull

Here we are using the distance of each seed

@@

### Calculate the mean and variance for these weibull distributions based on their estimated parameters

meanvar.weibull <- function(shape, scale){

  meanweibull <- scale * gamma(1+(1/shape))

  varweibull <- (scale^2)*(gamma(1+(2/shape))-(gamma(1+(1/shape))^2))

  return(c(meanweibull, varweibull))
}

joint_weib %>% 
  mutate(meanweib = est.scale * gamma(1+(1/est.shape)),
         varweib = (est.scale^2)*(gamma(1+(2/est.shape))-(gamma(1+(1/est.shape))^2))) -> joint_weib

@@

joint_weib %>%
  group_by(model) %>%
  ggplot(., aes(x = model, y = meanweib)) +
  geom_violin() +
  geom_jitter(data = joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  #geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(y = "Mean") +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL -> weib_mean

joint_weib %>%
  group_by(model) %>%
  ggplot(., aes(x = model, y = varweib)) +
  geom_violin() +
  geom_jitter(data = joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  labs(y = "Variance") +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL-> weib_variance

plot_grid(weib_shape, weib_scale, weib_mean, weib_variance, ncol = 4)

@@

```{r}
z.joint_weib <- joint_weib %>% 
  mutate(est.shape = scale(est.shape),
         est.scale = scale(est.scale),
         meanweib = scale(meanweib),
         varweib = scale(varweib))

z.joint_weib %>%
  group_by(model) %>%
  #sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(data = z.joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  #geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(y = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL -> weib_shape

z.joint_weib %>%
  group_by(model) %>%
  #sample_n(., 200) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(data = z.joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  labs(y = "Scale") +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL-> weib_scale

z.joint_weib %>%
  group_by(model) %>%
  ggplot(., aes(x = model, y = meanweib)) +
  geom_violin() +
  geom_jitter(data = z.joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  #geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(y = "Mean") +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL -> weib_mean

z.joint_weib %>%
  group_by(model) %>%
  ggplot(., aes(x = model, y = varweib)) +
  geom_violin() +
  geom_jitter(data = z.joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  labs(y = "Variance") +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL-> weib_variance

plot_grid(weib_shape, weib_scale, weib_mean, weib_variance, ncol = 4)

```{r}
z.joint_weib %>% 
  pivot_longer(., cols = c(est.shape, est.scale, meanweib, varweib)) %>% 
  ggplot(., aes(x = name, y = value, color = model)) +
  geom_boxplot() +
  theme_bw()
